---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# techme

<!-- badges: start -->
<!-- badges: end -->

The goal of techme is to supply basic data sets and toolsets to generate research report.

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("huhuaping/techme")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
require(techme)
data("varsList")
head(varsList)
```

## Data set list and source

### Basic

```{r,echo=FALSE, message=FALSE}
require(techme)
data("varsList")
data("BasicProvince")
data("queryTianyan")
data("ProvinceCity")

```

**`varsList`**：A data set containing all variables and additional information, such as unit, chn_name, eng_name etc., with wide data format.

- Totally `r dim(varsList)[2]` columns including: `r paste0(names(varsList), collapse =", ")`。

- Totally `r dim(varsList)[1]` rows。


**`BasicProvince`**：A data set containing basic information of province and its region, with wide data format.

- Totally `r dim(BasicProvince)[2]` columns including: `r paste0(names(BasicProvince), collapse =", ")`。

- Totally `r dim(BasicProvince)[1]` rows。


**`ProvinceCity`**：A data set containing Province and City of china.

- Totally `r dim(ProvinceCity)[2]` columns including: `r paste0(names(ProvinceCity), collapse =", ")`。

- Totally `r dim(ProvinceCity)[1]` rows。


**`queryTianyan`**：A data set containing basic info of institution enrolled in officer administrator.

- Totally `r dim(queryTianyan)[2]` columns including: `r paste0(names(queryTianyan), collapse =", ")`。

- Totally `r dim(queryTianyan)[1]` rows。


### Yearbook


#### Data from Rural Yearbook

```{r,echo=FALSE}
data("AgriMachine")
data("AgriFertilizer")
data("AgriPlastic")
data("AgriPesticide")
```

**`AgriMachine`**：A **long format** data set containing Agricultural Machine statistics .

- Totally `r dim(AgriMachine)[2]` columns including: `r paste0(names(AgriMachine), collapse =", ")`。

- Totally `r dim(AgriMachine)[1]` rows。

- Years range from `r min(AgriMachine$year)` to `r max(AgriMachine$year)` 

- Variables including: `r paste0(sort(unique(AgriMachine$variables)), collapse =", ")`


**`AgriFertilizer`**：A **long format** data set containing Agricultural Fertilizer statistics .

- Totally `r dim(AgriFertilizer)[2]` columns including: `r paste0(names(AgriFertilizer), collapse =", ")`。

- Totally `r dim(AgriFertilizer)[1]` rows。

- Years range from `r min(AgriFertilizer$year)` to `r max(AgriFertilizer$year)` 

- Variables including: `r paste0(sort(unique(AgriFertilizer$variables)), collapse =", ")`


**`AgriPlastic`**：A **long format** data set containing Agricultural Plastic statistics .

- Totally `r dim(AgriPlastic)[2]` columns including: `r paste0(names(AgriPlastic), collapse =", ")`。

- Totally `r dim(AgriPlastic)[1]` rows。

- Years range from `r min(AgriPlastic$year)` to `r max(AgriPlastic$year)` 

- Variables including: `r paste0(sort(unique(AgriPlastic$variables)), collapse =", ")`


**`AgriPesticide`**：A **long format** data set containing Agricultural Pesticide statistics .

- Totally `r dim(AgriPesticide)[2]` columns including: `r paste0(names(AgriPesticide), collapse =", ")`。

- Totally `r dim(AgriPesticide)[1]` rows。

- Years range from `r min(AgriPesticide$year)` to `r max(AgriPesticide$year)` 

- Variables including: `r paste0(sort(unique(AgriPesticide$variables)), collapse =", ")`

#### Data from Sci-Tech Yearbook


```{r,echo=FALSE}
data("RDIntense")
data("RDActivity")
data("IndustryOperation")
data("IndustryRD")
data("IndustryTrade")
data("MarketPull")
data("MarketPush")

```

**`RDIntense`**：A **long format** data set containing R&D Intense statistics.

- Totally `r dim(RDIntense)[2]` columns including: `r paste0(names(RDIntense), collapse =", ")`。

- Totally `r dim(RDIntense)[1]` rows。

- Years range from `r min(RDIntense$year)` to `r max(RDIntense$year)` 

- Variables including: `r paste0(sort(unique(RDIntense$variables)), collapse =", ")`

**`RDActivity`**：A **long format** data set containing R&D Activity statistics .

- Totally `r dim(RDActivity)[2]` columns including: `r paste0(names(RDActivity), collapse =", ")`。

- Totally `r dim(RDActivity)[1]` rows。

- Years range from `r min(RDActivity$year)` to `r max(RDActivity$year)` 

- Variables including: `r paste0(sort(unique(RDActivity$variables)), collapse =", ")`


**`IndustryOperation`**：A **long format** data set containing Industry Operation statistics .

- Totally `r dim(IndustryOperation)[2]` columns including: `r paste0(names(IndustryOperation), collapse =", ")`。

- Totally `r dim(IndustryOperation)[1]` rows。

- Years range from `r min(IndustryOperation$year)` to `r max(IndustryOperation$year)` 

- Variables including: `r paste0(sort(unique(IndustryOperation$variables)), collapse =", ")`


**`IndustryRD`**：A **long format** data set containing Industry R&D statistics .

- Totally `r dim(IndustryRD)[2]` columns including: `r paste0(names(IndustryRD), collapse =", ")`。

- Totally `r dim(IndustryRD)[1]` rows。

- Years range from `r min(IndustryRD$year)` to `r max(IndustryRD$year)` 

- Variables including: `r paste0(sort(unique(IndustryRD$variables)), collapse =", ")`

**`IndustryTrade`**：A **long format** data set containing Industry Trade statistics .

- Totally `r dim(IndustryTrade)[2]` columns including: `r paste0(names(IndustryTrade), collapse =", ")`。

- Totally `r dim(IndustryTrade)[1]` rows。

- Years range from `r min(IndustryTrade$year)` to `r max(IndustryTrade$year)` 

- Variables including: `r paste0(sort(unique(IndustryTrade$variables)), collapse =", ")`


**`MarketPull`**：A **long format** data set containing Tech Market Pull statistics .

- Totally `r dim(MarketPull)[2]` columns including: `r paste0(names(MarketPull), collapse =", ")`。

- Totally `r dim(MarketPull)[1]` rows。

- Years range from `r min(MarketPull$year)` to `r max(MarketPull$year)` 

- Variables including: `r paste0(sort(unique(MarketPull$variables)), collapse =", ")`

**`MarketPush`**：A **long format** data set containing Tech Market Push statistics .

- Totally `r dim(MarketPush)[2]` columns including: `r paste0(names(MarketPush), collapse =", ")`。

- Totally `r dim(MarketPush)[1]` rows。

- Years range from `r min(MarketPush$year)` to `r max(MarketPush$year)` 

- Variables including: `r paste0(sort(unique(MarketPush$variables)), collapse =", ")`

#### Data from China National Yearbook

```{r,echo=FALSE}
data("PublicBudget")
```

**`PublicBudget`**：A **long format** data set containing Public Budget statistics.

- Totally `r dim(PublicBudget)[2]` columns including: `r paste0(names(PublicBudget), collapse =", ")`。

- Totally `r dim(PublicBudget)[1]` rows。

- Years range from `r min(PublicBudget$year)` to `r max(PublicBudget$year)` 

- Variables including: `r paste0(sort(unique(PublicBudget$variables)), collapse =", ")`

### Public site

#### Data from MOST

Several data set sources from Ministry of Sci-Tech (MOST).


```{r,echo=FALSE}
data("PubNKRDP")
data("PubAgriParkList")
data("PubAgriParkEval")
```

**`PubNKRDP`**：A **wide format** data set containing Details of National Key R&D Plans(NKRDP) statistics.

- Totally `r dim(PubNKRDP)[2]` columns including: `r paste0(names(PubNKRDP), collapse =", ")`。

- Totally `r dim(PubNKRDP)[1]` rows。

- Years range from `r min(PubNKRDP$year)` to `r max(PubNKRDP$year)` 


**`PubAgriParkList`**：A **wide format** data set containing Details of Approved List of National Agricultural Sci-tech Park.

- Totally `r dim(PubAgriParkList)[2]` columns including: `r paste0(names(PubAgriParkList), collapse =", ")`。

- Totally `r dim(PubAgriParkList)[1]` rows。

- Years (Batch) range from `r min(PubAgriParkList$batch)` to `r max(PubAgriParkList$batch)` 

**`PubAgriParkEval`**：A **wide format** data set containing Details of Evaluation result of National Agricultural Sci-tech Park.

- Totally `r dim(PubAgriParkEval)[2]` columns including: `r paste0(names(PubAgriParkEval), collapse =", ")`。

- Totally `r dim(PubAgriParkEval)[1]` rows。

- Years range from `r min(PubAgriParkEval$year)` to `r max(PubAgriParkEval$year)` 

#### Data from MOA or MOE


```{r,echo=FALSE}
data("PubObsStation")
```

Several data set sources from Ministry of Agriculture (MOA) or Ministry of Education (MOE).

**`PubObsStation`**：A **wide format** data set containing Details of Evaluation result of National Agricultural Sci-tech Details list of Observe Stations of MOA and MOE.

- Totally `r dim(PubObsStation)[2]` columns including: `r paste0(names(PubObsStation), collapse =", ")`。

- Totally `r dim(PubObsStation)[1]` rows。

- Years range from `r min(PubObsStation$year)` to `r max(PubObsStation$year)` 



