---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# techme

<!-- badges: start -->
<!-- badges: end -->

The goal of techme is to supply basic data sets and toolsets to generate research report.

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("huhuaping/techme")
```
## Data set list and source

### Basic

```{r,echo=FALSE}
require(techme)
data("BasicProvince")
data("queryTianyan")
data("ProvinceCity")

```

**`BasicProvince`**：A data set containing basic information of province and its region, with wide data format.

- Totally `r dim(BasicProvince)[2]` columns including: `r paste0(names(BasicProvince), collapse =", ")`。

- Totally `r dim(BasicProvince)[1]` rows。


**`ProvinceCity`**：A data set containing Province and City of china.

- Totally `r dim(ProvinceCity)[2]` columns including: `r paste0(names(ProvinceCity), collapse =", ")`。

- Totally `r dim(ProvinceCity)[1]` rows。


**`queryTianyan`**：A data set containing basic info of institution enrolled in officer administrator.

- Totally `r dim(queryTianyan)[2]` columns including: `r paste0(names(queryTianyan), collapse =", ")`。

- Totally `r dim(queryTianyan)[1]` rows。


### Yearbook


#### Data from Rural Yearbook

```{r,echo=FALSE}
data("AgriMachine")
data("AgriMachine")
data("AgriFertilizer")
data("AgriPlastic")
data("AgriPesticide")
```

**`AgriMachine`**：A **long format** data set containing Agricultural Machine statistics .

- Years range in `min(AgriMachine$year)` to `max(AgriMachine$year)` 

- Totally `r dim(AgriMachine)[2]` columns including: `r paste0(names(AgriMachine), collapse =", ")`。

- Totally `r dim(AgriMachine)[1]` rows。



### Public site

## Example

This is a basic example which shows you how to solve a common problem:


