---
title: "02-Techme数据集"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{techme data set}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(techme)
```

This is whole all variables list of this data base:

```{r}
data("varsList")
head(varsList)
```

# Basic

```{r,echo=FALSE, message=FALSE}
require(techme)
#require(tidyverse)
#require(purrr)
require(knitr)
library(magrittr)
library(dplyr)
data("varsList")
data("BasicProvince")
data("queryTianyan")
data("ProvinceCity")

```

## varsList

**`varsList`**：A data set containing all variables and additional information, such as unit, chn_name, eng_name etc., with wide data format.

- Totally `r dim(varsList)[2]` columns including: `r paste0(names(varsList), collapse =", ")`.

- Totally `r dim(varsList)[1]` rows.

```{r}
varsList %>%
  sample_n(size = 10) %>%
  kable()
```

## BasicProvince

**`BasicProvince`**：A data set containing basic information of province and its region, with wide data format.

- Totally `r dim(BasicProvince)[2]` columns including: `r paste0(names(BasicProvince), collapse =", ")`.

- Totally `r dim(BasicProvince)[1]` rows.

```{r}
BasicProvince %>%
  sample_n(size = 10) %>%
  kable()
```

## ProvinceCity

**`ProvinceCity`**：A data set containing Province and City of china.

- Totally `r dim(ProvinceCity)[2]` columns including: `r paste0(names(ProvinceCity), collapse =", ")`.

- Totally `r dim(ProvinceCity)[1]` rows.

```{r}
ProvinceCity %>%
  sample_n(size = 10) %>%
  kable()
```

## queryTianyan

**`queryTianyan`**：A data set containing basic info of institution enrolled in officer administrator.

- Totally `r dim(queryTianyan)[2]` columns including: `r paste0(names(queryTianyan), collapse =", ")`.

- Totally `r dim(queryTianyan)[1]` rows.

```{r}
queryTianyan %>%
  sample_n(size = 10) %>%
  kable()
```

# Yearbook


## Source from Rural Yearbook

```{r,echo=FALSE}
data("AgriMachine")
data("AgriFertilizer")
data("AgriPlastic")
data("AgriPesticide")
```

### AgriMachine

**`AgriMachine`**：A **long format** data set containing Agricultural Machine statistics .

- Totally `r dim(AgriMachine)[2]` columns including: `r paste0(names(AgriMachine), collapse =", ")`.

- Totally `r dim(AgriMachine)[1]` rows.

- Years range from `r min(AgriMachine$year)` to `r max(AgriMachine$year)` 

- Variables including: `r paste0(sort(unique(AgriMachine$variables)), collapse =", ")`

```{r}
AgriMachine %>%
  sample_n(size = 10) %>%
  kable()
```


### AgriFertilizer

**`AgriFertilizer`**：A **long format** data set containing Agricultural Fertilizer statistics .

- Totally `r dim(AgriFertilizer)[2]` columns including: `r paste0(names(AgriFertilizer), collapse =", ")`.

- Totally `r dim(AgriFertilizer)[1]` rows.

- Years range from `r min(AgriFertilizer$year)` to `r max(AgriFertilizer$year)` 

- Variables including: `r paste0(sort(unique(AgriFertilizer$variables)), collapse =", ")`

```{r}
AgriFertilizer %>%
  sample_n(size = 10) %>%
  kable()
```

### AgriPlastic

**`AgriPlastic`**：A **long format** data set containing Agricultural Plastic statistics .

- Totally `r dim(AgriPlastic)[2]` columns including: `r paste0(names(AgriPlastic), collapse =", ")`.

- Totally `r dim(AgriPlastic)[1]` rows.

- Years range from `r min(AgriPlastic$year)` to `r max(AgriPlastic$year)` 

- Variables including: `r paste0(sort(unique(AgriPlastic$variables)), collapse =", ")`

```{r}
AgriPlastic %>%
  sample_n(size = 10) %>%
  kable()
```

### AgriPesticide

**`AgriPesticide`**：A **long format** data set containing Agricultural Pesticide statistics .

- Totally `r dim(AgriPesticide)[2]` columns including: `r paste0(names(AgriPesticide), collapse =", ")`.

- Totally `r dim(AgriPesticide)[1]` rows.

- Years range from `r min(AgriPesticide$year)` to `r max(AgriPesticide$year)` 

- Variables including: `r paste0(sort(unique(AgriPesticide$variables)), collapse =", ")`

```{r}
AgriPesticide %>%
  sample_n(size = 10) %>%
  kable()
```

## Source from Sci-Tech Yearbook


```{r,echo=FALSE}
# data("RDIntense") from public site
data("RDActivity")
data("IndustryOperation")
data("IndustryRD")
data("IndustryTrade")
data("MarketPull")
data("MarketPush")

```



### RDIntense

来自于中国政府网历年“全国科技经费投入统计公报”：

- 2021年全国科技经费投入统计[公报](https://www.gov.cn/xinwen/2022-08/31/content_5707547.htm)

- 2020年全国科技经费投入统计[公报](https://www.gov.cn/xinwen/2021-09/22/content_5638653.htm)

> 说明：《中国科技统计年鉴》也有数据发布，但是把经费和强度指标分别存放了，不符合本数据包的更新流程。

**`RDIntense`**：A **long format** data set containing R&D Intense statistics.

- Totally `r dim(RDIntense)[2]` columns including: `r paste0(names(RDIntense), collapse =", ")`.

- Totally `r dim(RDIntense)[1]` rows.

- Years range from `r min(RDIntense$year)` to `r max(RDIntense$year)` 

- Variables including: `r paste0(sort(unique(RDIntense$variables)), collapse =", ")`

```{r}
RDIntense %>%
  sample_n(size = 10) %>%
  kable()
```

### RDActivity

**`RDActivity`**：A **long format** data set containing R&D Activity statistics .

- Totally `r dim(RDActivity)[2]` columns including: `r paste0(names(RDActivity), collapse =", ")`.

- Totally `r dim(RDActivity)[1]` rows.

- Years range from `r min(RDActivity$year)` to `r max(RDActivity$year)` 

- Variables including: `r paste0(sort(unique(RDActivity$variables)), collapse =", ")`

```{r}
RDActivity %>%
  sample_n(size = 10) %>%
  kable()
```


### IndustryOperation

**`IndustryOperation`**：A **long format** data set containing Industry Operation statistics .

- Totally `r dim(IndustryOperation)[2]` columns including: `r paste0(names(IndustryOperation), collapse =", ")`.

- Totally `r dim(IndustryOperation)[1]` rows.

- Years range from `r min(IndustryOperation$year)` to `r max(IndustryOperation$year)` 

- Variables including: `r paste0(sort(unique(IndustryOperation$variables)), collapse =", ")`

```{r}
IndustryOperation %>%
  sample_n(size = 10) %>%
  kable()
```

### IndustryRD

**`IndustryRD`**：A **long format** data set containing Industry R&D statistics .

- Totally `r dim(IndustryRD)[2]` columns including: `r paste0(names(IndustryRD), collapse =", ")`.

- Totally `r dim(IndustryRD)[1]` rows.

- Years range from `r min(IndustryRD$year)` to `r max(IndustryRD$year)` 

- Variables including: `r paste0(sort(unique(IndustryRD$variables)), collapse =", ")`

```{r}
IndustryRD %>%
  sample_n(size = 10) %>%
  kable()
```



### MarketPull

**`MarketPull`**：A **long format** data set containing Tech Market Pull statistics .

> **说明**：数据包括合同数（`amount-xxxx.xlsx`）和金额（`funds-xxxx.xlsx`）两个表格来源，需要独立更新全部xlsx后，再读取整合为一个数据表。

- Totally `r dim(MarketPull)[2]` columns including: `r paste0(names(MarketPull), collapse =", ")`.

- Totally `r dim(MarketPull)[1]` rows.

- Years range from `r min(MarketPull$year)` to `r max(MarketPull$year)` 

- Variables including: `r paste0(sort(unique(MarketPull$variables)), collapse =", ")`

```{r}
MarketPull %>%
  sample_n(size = 10) %>%
  kable()
```

### MarketPush

**`MarketPush`**：A **long format** data set containing Tech Market Push statistics .

> **说明**：数据包括合同数（`amount-xxxx.xlsx`）和金额（`funds-xxxx.xlsx`）两个表格来源，需要独立更新全部xlsx后，再读取整合为一个数据表。

- Totally `r dim(MarketPush)[2]` columns including: `r paste0(names(MarketPush), collapse =", ")`.

- Totally `r dim(MarketPush)[1]` rows.

- Years range from `r min(MarketPush$year)` to `r max(MarketPush$year)` 

- Variables including: `r paste0(sort(unique(MarketPush$variables)), collapse =", ")`

```{r}
MarketPush %>%
  sample_n(size = 10) %>%
  kable()
```

### IndustryTrade

**`IndustryTrade`**：A **long format** data set containing Industry Trade statistics .

> 说明：2018年以后年鉴不再发布该数据！

- Totally `r dim(IndustryTrade)[2]` columns including: `r paste0(names(IndustryTrade), collapse =", ")`.

- Totally `r dim(IndustryTrade)[1]` rows.

- Years range from `r min(IndustryTrade$year)` to `r max(IndustryTrade$year)` 

- Variables including: `r paste0(sort(unique(IndustryTrade$variables)), collapse =", ")`

```{r}
IndustryTrade %>%
  sample_n(size = 10) %>%
  kable()
```

## Source from China National Yearbook

```{r,echo=FALSE}
data("PublicBudget")
```

### PublicBudget

**`PublicBudget`**：A **long format** data set containing Public Budget statistics.

> **说明**：来源于《中国统计年鉴》，表7-6 分地区一般公共预算支出。我们只整理更新如下列变量："地方一般公共预算支出","教育支出","科学技术支出","农林水支出"。

- Totally `r dim(PublicBudget)[2]` columns including: `r paste0(names(PublicBudget), collapse =", ")`.

- Totally `r dim(PublicBudget)[1]` rows.

- Years range from `r min(PublicBudget$year)` to `r max(PublicBudget$year)` 

- Variables including: `r paste0(sort(unique(PublicBudget$variables)), collapse =", ")`

```{r,echo=FALSE}
data("PublicBudget")

PublicBudget %>%
  sample_n(size = 10) %>%
  kable()
```

## Source from Livestock Yearbook


**`LivestockBreeding`**：A **long format** data set containing Livestock Breeding statistics.

- Totally `r dim(LivestockBreeding)[2]` columns including: `r paste0(names(LivestockBreeding), collapse =", ")`.

- Totally `r dim(LivestockBreeding)[1]` rows.

- Years range from `r min(LivestockBreeding$year)` to `r max(LivestockBreeding$year)` 

- Variables including: `r paste0(head(sort(unique(LivestockBreeding$variables)),20), collapse =", ")`（top 20 of totally `r glue::glue("{length(unique(LivestockBreeding$variables))} variables")`.

```{r,echo=FALSE}
data("LivestockBreeding")

LivestockBreeding %>%
  sample_n(size = 10) %>%
  kable()
```

# Public site

## Source from Government site

### some data set

## Source from MOST

Several data set sources from Ministry of Sci-Tech (MOST).


```{r,echo=FALSE}
data("PubNKRDP")
data("PubAgriParkList")
data("PubAgriParkEval")
```

### PubNKRDP

**`PubNKRDP`**：A **wide format** data set containing Details of National Key R&D Plans(NKRDP) statistics.

- Totally `r dim(PubNKRDP)[2]` columns including: `r paste0(names(PubNKRDP), collapse =", ")`.

- Totally `r dim(PubNKRDP)[1]` rows.

- Years range from `r min(PubNKRDP$year)` to `r max(PubNKRDP$year)` 

```{r}
PubNKRDP %>%
  sample_n(size = 10) %>%
  kable()
```

### PubAgriParkList

> **说明**：本数据集直接在`techme`包开发环境下进行原始数据（data-raw）的清洗和整理（"techme/data-raw/public-site/agri-park/03-list-raw/"）；然后清洗后的xlsx文件复制到（"techme/data-raw/data-tidy/public-site/agri-park/xlsx/"），最后再经由"techme/data-raw/wfl_useData_agriPark.R"进行批量读取和数据集编译。

**`PubAgriParkList`**：A **wide format** data set containing Details of Approved List of National Agricultural Sci-tech Park.

- Totally `r dim(PubAgriParkList)[2]` columns including: `r paste0(names(PubAgriParkList), collapse =", ")`.

- Totally `r dim(PubAgriParkList)[1]` rows.

- Years (Batch) range from `r min(PubAgriParkList$batch)` to `r max(PubAgriParkList$batch)` 

```{r}
PubAgriParkList %>%
  sample_n(size = 10) %>%
  kable()
```

### PubAgriParkEval

> **说明**：本数据集直接在`techme`包开发环境下进行原始数据（data-raw）的清洗和整理（"techme/data-raw/public-site/agri-park/02-eval-raw/"）；然后清洗后的xlsx文件复制到（"techme/data-raw/data-tidy/public-site/agri-park/xlsx/"），最后再经由"techme/data-raw/wfl_useData_agriPark.R"进行批量读取和数据集编译。

**`PubAgriParkEval`**：A **wide format** data set containing Details of Evaluation result of National Agricultural Sci-tech Park.

- Totally `r dim(PubAgriParkEval)[2]` columns including: `r paste0(names(PubAgriParkEval), collapse =", ")`.

- Totally `r dim(PubAgriParkEval)[1]` rows.

- Years range from `r min(PubAgriParkEval$year)` to `r max(PubAgriParkEval$year)` 

```{r}
PubAgriParkEval %>%
  sample_n(size = 10) %>%
  kable()
```


### PubAgriParkCheck

> **说明**：本数据集直接在`techme`包开发环境下进行原始数据（data-raw）的清洗和整理（"techme/data-raw/public-site/agri-park/01-check-raw/"）；然后清洗后的xlsx文件复制到（"techme/data-raw/data-tidy/public-site/agri-park/xlsx/"），最后再经由"techme/data-raw/wfl_useData_agriPark.R"进行批量读取和数据集编译。

**`PubAgriParkCheck`**：A **wide format** data set containing Details of Check result of National Agricultural Sci-tech Park.

- Totally `r dim(PubAgriParkCheck)[2]` columns including: `r paste0(names(PubAgriParkCheck), collapse =", ")`.

- Totally `r dim(PubAgriParkCheck)[1]` rows.

- Years range from `r min(PubAgriParkCheck$year)` to `r max(PubAgriParkCheck$year)` 

```{r}
PubAgriParkCheck %>%
  sample_n(size = 10) %>%
  kable()
```

### HitechFirmsPub

**数据来源**：科学技术部火炬高技术产业开发中心<http://www.innocom.gov.cn>。

**说明**：本数据集直接在`tech-report`项目下进行原始数据（data-raw）的清洗和整理（"tech-report/data-raw/public-site/torch-innocom/xlsx/"）；然后清洗后的xlsx文件复制到（"tech-report/data-raw/data-tidy/public-site/torch-innocom/xlsx/"）。最后再一次复制到`techme`包开发环境下的"techme/data-raw/data-tidy/public-site/torch-innocom/xlsx/"，再经由"techme/data-raw/wfl_useData_HitechFirms.R"进行批量读取和数据集编译。

**`HitechFirmsPub`**：A **wide format** data set containing Details of  Hi-tech Firms Numbers on Public Site.

- Totally `r dim(HitechFirmsPub)[2]` columns including: `r paste0(names(HitechFirmsPub), collapse =", ")`.

- Totally `r dim(HitechFirmsPub)[1]` rows.

- Years range from `r min(HitechFirmsPub$year)` to `r max(HitechFirmsPub$year)` 

```{r}
HitechFirmsPub %>%
  sample_n(size = 10) %>%
  kable()
```

### PubOpenShare

**数据来源**：科学技术部火炬高技术产业开发中心<http://www.innocom.gov.cn>。

**说明**：本数据集直接在`techme`项目下进行原始数据（data-raw）的清洗和整理（"techme/data-raw/public-site/most-jcs-open-share/xlsx/"），再经由"techme/data-raw/public-site/most-jcs-open-share/wfl-PubOpenShare.R"进行批量读取和数据集编译。

**`PubOpenShare`**：A **wide format** data set containing Details of Evaluation result of Major Scientific Infrastructure and Large-scale Scientific Instruments Sharing.

- Totally `r dim(PubOpenShare)[2]` columns including: `r paste0(names(PubOpenShare), collapse =", ")`.

- Totally `r dim(PubOpenShare)[1]` rows.

- Years range from `r min(PubOpenShare$year)` to `r max(PubOpenShare$year)` 

```{r}
PubOpenShare %>%
  sample_n(size = 10) %>%
  kable()
```


## Source from MOA or MOE


```{r,echo=FALSE}
data("PubObsStation")
```

Several data set sources from Ministry of Agriculture (MOA) or Ministry of Education (MOE).

### PubObsStation

**`PubObsStation`**：A **wide format** data set containing Details of Evaluation result of National Agricultural Sci-tech Details list of Observe Stations of MOA and MOE.

- Totally `r dim(PubObsStation)[2]` columns including: `r paste0(names(PubObsStation), collapse =", ")`.

- Totally `r dim(PubObsStation)[1]` rows.

- Years range from `r min(PubObsStation$year)` to `r max(PubObsStation$year)` 

<!---CARS from MOA---->

```{r}
data("PubCars")
```

**`PubCars`**：A **wide format** data set containing Details of China Agricultural Research System(CARS) from MOA.

- Totally `r dim(PubCars)[2]` columns including: `r paste0(names(PubCars), collapse =", ")`.

- Totally `r dim(PubCars)[1]` rows.

- Years range from `r min(PubCars$year)` to `r max(PubCars$year)` 

```{r}
PubObsStation %>%
  sample_n(size = 10) %>%
  kable()
```

### PubAgriMarket

```{r,echo=FALSE}
data("PubAgriMarket")
```

> **说明**：本数据集整理农业农村部定点市场认定 / 取消名单（`data-raw/public-site/moa-agri-market/`）。2018、2024 年 YAML 经 `code-moa-agri-market-yaml.R` 展开为 tidy xlsx，再由 `wfl-PubAgriMarket.R` 编译。`type` 为认定名单 / 取消名单；新疆生产建设兵团记为新疆。

**`PubAgriMarket`**：A **wide format** data set containing MOA designated wholesale markets from the 2018 review and 2024 re-inspection notices.

- Totally `r dim(PubAgriMarket)[2]` columns including: `r paste0(names(PubAgriMarket), collapse =", ")`.

- Totally `r dim(PubAgriMarket)[1]` rows.

- Years: `r paste(sort(unique(PubAgriMarket$year)), collapse = ", ")`

- `type` values: 认定名单 / 取消名单。

```{r}
PubAgriMarket %>%
  count(year, type) %>%
  tidyr::pivot_wider(names_from = type, values_from = n, values_fill = 0) %>%
  kable()
```

### PubAgriTechDemoBase

```{r,echo=FALSE}
data("PubAgriTechDemoBase")
```

> **说明**：本数据集合并两套公示口径（`data-raw/public-site/moa-agritech-demo-base/`）。2020、2025 年 YAML 经 `code-moa-agritech-demo-base-yaml.R` 展开为 tidy xlsx，再由 `wfl-PubAgriTechDemoBase.R` 编译。`source` 区分当前口径（现代农业科技试验示范基地）与历史口径（国家农业科技示范展示基地）；2025 的 `type` 为种植业 / 畜牧兽医 / 渔业 / 农机 / 资源环境，2020 无分类。新疆生产建设兵团记为新疆。

**`PubAgriTechDemoBase`**：A **wide format** data set containing MOA agricultural sci-tech demonstration bases from the 2020 historical list and the 2025 first-batch notice.

- Totally `r dim(PubAgriTechDemoBase)[2]` columns including: `r paste0(names(PubAgriTechDemoBase), collapse =", ")`.

- Totally `r dim(PubAgriTechDemoBase)[1]` rows.

- Years: `r paste(sort(unique(PubAgriTechDemoBase$year)), collapse = ", ")`

- `source` values: 现代农业科技试验示范基地 / 国家农业科技示范展示基地。

```{r}
PubAgriTechDemoBase %>%
  count(year, source) %>%
  tidyr::pivot_wider(names_from = source, values_from = n, values_fill = 0) %>%
  kable()
```

### PubGeneticResource

```{r,echo=FALSE}
data("PubGeneticResource")
```

> **说明**：本数据集合并两条年度批次公示口径（`data-raw/public-site/moa-genetic-resource/`），由 `wfl-PubGeneticResource.R` 编译。`type` 同时收录农作物 / 农业微生物，以及畜禽保种场 / 畜禽基因库 / 畜禽保护区 / 畜禽变更。全量库圃快照见 `PubGeneticResourceCrop`。

**`PubGeneticResource`**：A **wide format** data set containing approved national genetic-resource bases from MOA year-batch notices (crop / microbe banks and livestock conservation units).

- Totally `r dim(PubGeneticResource)[2]` columns including: `r paste0(names(PubGeneticResource), collapse =", ")`.

- Totally `r dim(PubGeneticResource)[1]` rows.

- Years range from `r min(PubGeneticResource$year)` to `r max(PubGeneticResource$year)`

- `type` values: 农作物 / 农业微生物；畜禽保种场 / 畜禽基因库 / 畜禽保护区 / 畜禽变更。

```{r}
PubGeneticResource %>%
  count(year, type) %>%
  tidyr::pivot_wider(names_from = type, values_from = n, values_fill = 0) %>%
  kable()
```

### PubGeneticResourceCrop

```{r,echo=FALSE}
data("PubGeneticResourceCrop")
```

> **说明**：本数据集在`techme`项目下参数化爬取全国农作物种质资源信息平台库圃列表（"techme/data-raw/public-site/moa-genetic-resource/"），清洗后的xlsx经由`wfl-PubGeneticResource.R`编译。与按年度批次公示的`PubGeneticResource`口径不同。

**`PubGeneticResourceCrop`**：A **wide format** data set containing the full list of national crop germplasm resource banks and nurseries.

- Totally `r dim(PubGeneticResourceCrop)[2]` columns including: `r paste0(names(PubGeneticResourceCrop), collapse =", ")`.

- Totally `r dim(PubGeneticResourceCrop)[1]` rows.

- Years range from `r min(PubGeneticResourceCrop$year)` to `r max(PubGeneticResourceCrop$year)`

```{r}
PubGeneticResourceCrop %>%
  sample_n(size = 10) %>%
  kable()
```

### PubMachineCountyCase

```{r,echo=FALSE}
data("PubMachineCountyCase")
```

> **说明**：本数据集在`techme`项目下整理农业农村部特色经济作物全程机械化生产模式与典型案例公示名单（"techme/data-raw/public-site/moa-machine-county/"），yaml 经 `code-moa-machine-county-case.R` 展开为 xlsx，再由 `wfl-PubMachineCounty.R` 编译。

**`PubMachineCountyCase`**：A **wide format** data set containing typical cases of full-process mechanization for specialty economic crops.

- Totally `r dim(PubMachineCountyCase)[2]` columns including: `r paste0(names(PubMachineCountyCase), collapse =", ")`.

- Totally `r dim(PubMachineCountyCase)[1]` rows.

- Years range from `r min(PubMachineCountyCase$year)` to `r max(PubMachineCountyCase$year)`

```{r}
PubMachineCountyCase %>%
  sample_n(size = 10) %>%
  kable()
```

### PubBreedingXmj

```{r,echo=FALSE}
data("PubBreedingXmj")
```

> **已弃用**：请改用 `PubXmjBreeding`。本对象为 2010–2020 快照，将在后续版本移除。

**`PubBreedingXmj`**：A **wide format** data set containing details of Officer' Livestock Breeding List from MOA (Xmj).

- Totally `r dim(PubBreedingXmj)[2]` columns including: `r paste0(names(PubBreedingXmj), collapse =", ")`.

- Totally `r dim(PubBreedingXmj)[1]` rows.

- Years range from `r min(PubBreedingXmj$year)` to `r max(PubBreedingXmj$year)`

### PubXmjBreeding

```{r,echo=FALSE}
data("PubXmjBreeding")
```

> **说明**：本数据集在 `techme` 项目下整理农业农村部国家畜禽核心育种场等公示名单（`data-raw/public-site/moa-xmj-breeding/`）。2010–2020 年由 `scrape-breeding.Rmd` 清洗（空省份已从旧快照回填）；2021 年起 YAML 经 `code-scrape-breeding.R` 展开为 tidy xlsx，再由 `wfl-PubXmjBreeding.R` 编译。这是当前唯一应使用的名单。

**`PubXmjBreeding`**：A **wide format** data set containing national core livestock breeding farms, elite multiplier farms, and core sire stations from MOA notices.

- Totally `r dim(PubXmjBreeding)[2]` columns including: `r paste0(names(PubXmjBreeding), collapse =", ")`.

- Totally `r dim(PubXmjBreeding)[1]` rows.

- Years range from `r min(PubXmjBreeding$year)` to `r max(PubXmjBreeding$year)`

```{r}
PubXmjBreeding %>%
  sample_n(size = 10) %>%
  kable()
```

### PubStandardXmj

```{r,echo=FALSE}
data("PubStandardXmj")
```

> **已弃用**：请改用 `PubXmjStandard`。本对象为 2010–2020 快照，将在后续版本移除。

**`PubStandardXmj`**：A **wide format** data set containing details of Officer' Livestock Standard List from MOA (Xmj).

- Totally `r dim(PubStandardXmj)[2]` columns including: `r paste0(names(PubStandardXmj), collapse =", ")`.

- Totally `r dim(PubStandardXmj)[1]` rows.

- Years range from `r min(PubStandardXmj$year)` to `r max(PubStandardXmj$year)`

### PubXmjStandard

```{r,echo=FALSE}
data("PubXmjStandard")
```

> **说明**：本数据集在 `techme` 项目下整理农业农村部畜禽养殖标准化示范场认定名单（`data-raw/public-site/moa-xmj-standard/`）。2010–2020 年由 `scrape-standard.Rmd` 清洗（无 2012 年公示）；2021 年起 YAML 经 `code-scrape-standard.R` 展开为 tidy xlsx，再由 `wfl-PubXmjStandard.R` 编译。这是当前唯一应使用的名单。

**`PubXmjStandard`**：A **wide format** data set containing livestock standardized demonstration farms from MOA designation notices.

- Totally `r dim(PubXmjStandard)[2]` columns including: `r paste0(names(PubXmjStandard), collapse =", ")`.

- Totally `r dim(PubXmjStandard)[1]` rows.

- Years range from `r min(PubXmjStandard$year)` to `r max(PubXmjStandard$year)`

```{r}
PubXmjStandard %>%
  sample_n(size = 10) %>%
  kable()
```

